---
title: "p8105_hw3_ql2370"
author: "QiLu"
date: "10/12/2019"
output: github_document
---

```{r setup}
library(tidyverse)
```


## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
janitor::clean_names(instacart)
```

Instacart is an online grocery service that allows you to shop online from local stores. In New York City, partner stores include Whole Foods, Fairway, and The Food Emporium. Instacart offers same-day delivery, and items that users purchase are delivered within 2 hours.
  
This dataset describes the order history of  “The Instacart Online Grocery Shopping 2017”, which has 1384617 objects and 15 variables including order id, product id, user id, reordered, days since prior order, department id, etc.  
  
For example, the order with order id 1 added totally 8 items which 4 of them were reordered, and this order was placed on Thursday 10 am. The same user placed the prior order 9 days ago. Also, the detailed products information was included in this dataset.


```{r}

aisle_rank = instacart %>%
  count(aisle, name = "n_aisle") %>% 
  mutate(rank = min_rank(desc(n_aisle)))

aisle_max = aisle_rank %>% 
  filter(rank(desc(n_aisle)) == 1)

aisle_size = count(aisle_rank)
aisle_size
aisle_max
```
  
  a) There were 134 aisles, and the most itmes ordered from "fresh vegetables".
  
```{r}

aisle_plot = aisle_rank %>% 
  filter(n_aisle > 10000)

ggplot(aisle_plot, aes(x= aisle, y = n_aisle, color = aisle)) + 
  geom_point() +
   theme(legend.position = "bottom")
```
  
  b) This is the plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered.



```{r}
baking_data = instacart %>% 
  filter(aisle == "baking ingredients" | aisle == "dog food care" | aisle == "packaged vegetables fruits") %>% 
  group_by(aisle, product_name) %>% 
  summarize(count = n()) %>% 
  mutate(rank = rank(desc(count))) %>% 
  filter(rank <= 3)

baking_data

```
  
  c) This is the table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
  
  
```{r}
apple_ice_cream_data = instacart %>% 
  filter(product_name =="Pink Lady Apples" | product_name == "Coffee Ice Cream") %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean
  )
  
apple_ice_cream_data
  
```
  
  d) This is the table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week.
  
  
  
## Problem 2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
janitor::clean_names(brfss_smart2010)

brfss_smart2010 = brfss_smart2010 %>% 
  filter(Topic == "Overall Health")

response_level = c("Poor","Good", "Fair", "Very good", "Excellent")
brfss_smart2010$Response = ordered(brfss_smart2010$Response, response_level)
```

```{r}
more_than_7_2002 = brfss_smart2010 %>% 
  filter(Year == "2002") %>% 
  group_by(Locationabbr) %>% 
  summarize(n = n()) %>% 
  filter(n > 7)
```
In 2002, those were states observed at 7 or more locations.
  
```{r}
more_than_7_2010 = brfss_smart2010 %>% 
  filter(Year == "2010") %>% 
  group_by(Locationabbr) %>% 
  summarize(n = n()) %>% 
  filter(n > 7)
```
In 2010, those were states observed at 7 or more locations.

```{r}
excellent_resp = brfss_smart2010 %>% 
  filter(Response == "Excellent") %>% 
  group_by(Year, Locationabbr) %>% 
  summarise( mean = mean(Data_value)) %>% 
  drop_na()

excellent_resp %>% 
  ggplot(aes(x = Year, y = mean, color = Locationabbr)) + 
    geom_point() + geom_line() + 
    theme(legend.position = "bottom")


```


Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
